---
title: "Cheat-Sheet 4"
author: "Polina Sorokina"
date: "February 13, 2019"
output: html_document
---

```{r setup, include=FALSE, echo = TRUE, warning=TRUE}
library(tidyverse)

```
#Exploratory Data Analysis


##Visualising distributions

We use a bar chart when examining a *categorical* variable.

```{r}

ggplot(data = diamonds) +
  geom_bar(mapping = aes(x = cut), fill ="steelblue") 

```

A *countinuous* variable can take any set of ordered values. To examine the distribution, we can use a histogram.

```{r}
ggplot(data = diamonds) +
  geom_histogram(mapping = aes(x = carat), binwidth = 0.5, fill="steelblue")
```

Zooming in on dimonds with a carat over 3.

```{r}
larger <- diamonds %>% filter(carat>3)

ggplot(larger, mapping = aes(x = carat)) + geom_histogram(binwidth = 0.1, fill="steelblue")
```


Overlaying multiple histograms in the same plot.

```{r}
ggplot(data = larger, mapping = aes(x = carat, colour = cut)) + geom_freqpoly(binwidth = 0.1)
```


####Missing values

Best solution to dealwith strange values is to replace them with NA, ggplot does not include strange values and gives a warning. Or missing values can be removed, using na.rm = TRUE.

```{r}
diamonds2 <- diamonds %>% 
  mutate(y = ifelse(y < 3 | y > 20, NA, y))

ggplot(data = diamonds2, mapping = aes(x = x, y = y)) + 
  geom_point(na.rm = TRUE)

```


Coparing a *continuous* and *categorical* values for the diamonds data set displaying density.

```{r}

ggplot(data = diamonds, mapping = aes(x = price, y = ..density..)) + 
  geom_freqpoly(mapping = aes(colour = cut), binwidth = 500)

```

Another look at the distribution of price by cut using geom_boxplot():

```{r}
ggplot(data = diamonds, mapping = aes(x = cut, y = price)) +
  geom_boxplot()

```

Showing a covariation between *categorical* variables:


```{r}

ggplot(data = diamonds) +
  geom_count(mapping = aes(x = cut, y = color))

```

Another way to showcase count:

```{r}
diamonds %>% 
  count(color, cut) %>%  
  ggplot(mapping = aes(x = color, y = cut)) +
    geom_tile(mapping = aes(fill = n))


```


Showcasing coveriation between two *continuous* variables.

```{r}

ggplot(data = diamonds) +
  geom_point(mapping = aes(x = carat, y = price))

```


