---
title: "Cheat-Sheet 5"
author: "Polina Sorokina"
date: "February 13, 2019"
output: html_document
---

```{r setup, include=FALSE, echo=TRUE, warning =FALSE}

library(tidyverse)  
library(cluster)    
library(factoextra)
```

##Preliminary Work


First, we download the data and remove all missing values.

```{r}
df <- USArrests
df <-na.omit(df)
```

Then we scale/standarize the data using a scale function.

```{r}
df <- scale(df)
```

The following visualization illistrates which states have large dissimilarities (red) versus those that appear to be failry similar (teal). With the help of get_dist and fviz_dist from the factoextra.


```{r}
distance <- get_dist(df)
fviz_dist(distance, gradient = list(low = "#00AFBB", mid = "white", high = "#FC4E07"))
```

Next, computing k-means clustering...

```{r}
k2 <- kmeans(df, centers = 2, nstart = 25)
str(k2)

```

Viewing results with fviz_cluster...

```{r}
fviz_cluster(k2, data = df)

```


##Finding the optimal numbe rof clusters

###Elbow method

```{r}
set.seed(123)

fviz_nbclust(df, kmeans, method = "wss")
```


###Average Silhouette Method

```{r}
fviz_nbclust(df, kmeans, method = "silhouette")
```


###Gap Statisitc Method

```{r}
set.seed(123)
gap_stat <- clusGap(df, FUN = kmeans, nstart = 25,
                    K.max = 10, B = 50)
fviz_gap_stat(gap_stat)
```


##Results

```{r}
set.seed(123)
final <- kmeans(df, 4, nstart = 25)
print(final)
fviz_cluster(final, data = df)
```


